Quantifying the importance of an inference model in Bayesian phylogenetics

### 2019-11-18 content.tex
EOD

\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single,
    label = {lst:create_alignment_params}, 
    caption = {Create an alignment.}
  ]
alignment_params <- create_alignment_params(
  clock_model = create_strict_clock_model(),
  site_model = create_jc69_site_model(),
  mutation_rate = 0.1,
  root_sequence = create_blocked_dna(length = 1000)
)
\end{lstlisting}

@@

RJCB, GL and RSE conceived the idea for the package. 
RJCB created, tested and revised the package.
GL done major contributions to the package.
RJCB wrote the first draft of the manuscript, 
GL and RSE contributed to revisions.

>>>>

\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single,
    label = {lst:create_alignment_params}, 
    caption = {Create an alignment.}
  ]
alignment_params <- create_alignment_params(
  sim_true_alignment_fun = get_sim_true_alignment_with_std_site_model_fun(
    mutation_rate = 0.1,
    site_model = create_jc69_site_model()
  ),
  root_sequence = create_blocked_dna(length = 1000),
  rng_seed = rng_seed
)
\end{lstlisting}

@@

RJCB, GL and RSE conceived the idea for the package. 
RJCB created, tested and revised the package.
GL provided major contributions to the package.
RJCB wrote the first draft of the manuscript, 
GL and RSE contributed to revisions.
